### 2023-11-15 CV2/general.tex
CV and papers

\section{Positions}
\begin{tabular}{rl}	
	\textsc{2021-Now}& Research Intern\\
	&Research Center for Trusted Artificial Intelligence\\
	&\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia\\
	\textsc{2022-2023}& Postdoctoral Researcher\\
	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
	\textsc{2022-2023}& Researcher\\
	&Laboratory of Advanced Combinatorics and Network Applications\\
	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia
\end{tabular}

>>>>

\section{Positions}
\begin{tabular}{rl}	
	\textsc{2023-Now}& Senior Researcher\\
	&\textbf{\href{https://research.yandex.com}{\color{black}Yandex Research}}, Moscow, Russia\\
	\textsc{2021-2023}& Research Intern\\
	&Research Center for Trusted Artificial Intelligence\\
	&\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia\\
	\textsc{2022-2023}& Postdoctoral Researcher\\
	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
	\textsc{2022}& Researcher\\
	&Laboratory of Advanced Combinatorics and Network Applications\\
	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia
\end{tabular}

### 2023-11-15 CV2/papers.tex
CV and papers

@@

@@

\item \textbf{Decentralized Saddle-Point Problems with Different Constants of Strong Convexity and Strong Concavity} (\href{}{\color{linkcolour}Dmitriy Metelev}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2206.00090}{\em \color{black}arXiv preprint (May 2022)}

>>>>

\item \textbf{Non-smooth setting of stochastic decentralized convex optimization problem over time-varying graphs} (\href{}{\color{linkcolour}Aleksandr Lobanov}, \href{}{\color{linkcolour}Andrew Veprikov}, \href{}{\color{linkcolour}Georgiy Konin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://link.springer.com/article/10.1007/s10287-023-00479-7}{\em \color{black}Computational Management Science}

@@

\item \textbf{Decentralized Saddle-Point Problems with Different Constants of Strong Convexity and Strong Concavity} (\href{}{\color{linkcolour}Dmitriy Metelev}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://link.springer.com/article/10.1007/s10287-023-00485-9}{\em \color{black}Computational Management Science}

@@
